Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations

### 2018-04-05 ApJ_submit_v2/response.txt

We agree and moved the paragraphs on climate to Section 5.

===============================================
Major Comments

General Comments:
1. No table listing the major parameters of the system is available. It would be nice to have a table like this (with the citation to the discovery paper listed) for easy reference. It was annoying to have to go somewhere else (or wait until a plane landed) and dig around to find information such as the stellar mass/radius, etc. since it was not easily accessible in this paper.

We have added the main stellar and planetary parameters to the introduction.

@@

Therefore, I think section 2.2 should be significantly expanded (or this info should be in 3.2.2) to explain what the authors have done to reduce the Spitzer data so that it is more easily reproduced. Especially since many people (and this referee in particular) are much more familiar with PLD methods rather than BLISS mapping type methods.

#

We have added the following additional description to Sections 2.2 and 3.2.2 to clarify these points:

Section 2.2:
We used the POET pipeline (Stevenson et al. 2012; Cubillos et al. 2013) to reduce the Spitzer data.  The pipeline starts by identifying and flagging bad pixels using a double-iteration 4-sigma outlier rejection routine along the time axis.  This is followed by performing 2D Gaussian centroiding on each frame, which is shown to provide the most precise centers for Spitzer data (Lust et al.  2014).  The target remains centered near the sweet spot for the entire AOR in each observation, with a maximum drift of 0.1 pixels.  Next, POET uses sub-pixel (5x-interpolated) aperture photometry (Harrington et al. 2007) to subtract the background and sum the flux within a specified radius.  Chosen from a grid of apertures between 2 and 4 pixels, we find that an aperture size of 2.75 pixels minimizes the residual noise in the light curve fits.  For the background, we use an annulus with inner and outer radii of 7 and 15 pixels, respectively.  The contaminating flux from the nearby star is within the same pixel as the target, so we included it in the photometry and corrected it in the light curve fits.  A similarly strategy has been applied to successfully analyze dozens of Spitzer data sets (e.g. Stevenson et al. 2010, 2012a, 2012b, 2014a, 2014b, 2016a, 2017a, Campo et al. 2011, Nymeyer et al. 2011, Cubillos et al. 2013, Blecic et al.  2013, Blecic et al. 2014, Diamond-Lowe et al. 2014).

Section 3.2.2:
Warm Spitzer's primary systematic is intrapixel sensitivity variations, where the photometry depends on the precise location of the stellar center within its pixel.  We fit this systematic using the Bilinearly-Interpolated Subpixel Sensitivity (BLISS) mapping technique (Stevenson et al. 2012a).  BLISS provides a flexible, non-analytic means to effectively weight the target flux by the spatial sensitivity variations within a pixel, while simultaneously fitting for other systematics and the physical parameters of the system.  As has been demonstrated by Ingalls et al. 2016, the POET pipeline with BLISS mapping can accurately model simulated Spitzer light curves with known physical parameters and produce reliable results.

@@

Several of the theorists on this paper have spoken up to say that they like the reminder of what the raw data look like, since they don't work with the data directly. We therefore decided to keep the figure, but made the suggested changes. The figure now shows the raw data plotted as a function of time (BJD_TDB).

****

7. In section 3.3, the authors state that for a subset of cases an MCMC was used to determine parameter uncertainties. Which subset? How were they chosen?

#
Since we considered so many different cases (four different phase variation models for broadband and spectroscopic light curves), we elected to run an MCMC only for cases where we report 68% confidence intervals on the model parameters. These include the transit models (for the transit depth) and the sine curve models (for the phase amplitude and offset reported in Table 2). We added this clarification to the text in Section 3.3.

@@

More discussion here is warranted to show conclusively that the larger than predicted noise is not biasing the data or results. (This may be as simple as showing that other works show similar effects or that there are other works with elevated red noise in all channels but have shown that this does not affect the end results).

#

This is a good point, and something that concerned us as well. We endeavor to explain more clearly here why our inferences about the spectroscopic light curves are not affected by the additional noise in the white light curve, and have also added this discussion to section 3.4.

An important consideration that we neglected to mention is that the astrophysical signal is wavelength dependent -- the eclipse depths increase by 50% from the bluest channel to the reddest channel.  But for the white light curve, we sum up the whole signal and fit it with a single phase curve model.  Therefore, we expect a systematic scatter in the phase curve due to the wavelength dependence of the astrophysical signal.  To make an order of magnitude estimate for the amplitude of this effect, we calculated the standard deviation of the dayside secondary eclipse depths in all wavelength channels. It is $\sim100$ ppm, which is comparable to the additional scatter we observed in the white light curve.

@@

#

This is a really subtle point and we are glad the referee raised it. Here is our clarification:

It is somewhat misleading to evaluate the presence or absence of a thermal inversion based on the brightness temperatures reported in Table 6. The reason is that these temperatures account for uncertainty in the *stellar* effective temperature (+/- 160 K), as described in section 5.1. Therefore, the uncertainties in the table are correlated with each other. If the stellar temperature is higher, all the brightness temperatures would be higher, and vice versa if the stellar temperature is lower. When we hold the stellar temperature fixed, the error bars on brightness temperature shrink substantially (for example, the error on the dayside WFC3 brightness temperature is +/-8 Kelvin), and the temperatures at different wavelengths are discrepant at more than 3 sigma confidence. This can also be seen by eye in Figure 7, where the Spitzer 4.5 micron point is significantly higher than the blackbody (dashed line).

To evaluate the presence or absence of a thermal inversion, we carry out a retrieval analysis with the temperature of the star held fixed.  Our statements about the inversion on the dayside and the lack of inversion on the nightside are motivated by the retrieval, not the simple calculation of brightness temperature. We added a few sentences to the end of section 5.1 and the bullet point in section 8 to clarify this point.

@@

****

13. Section 5.2.1: Dayside spectrum - Which spectrum in specific are the authors trying to fit. Are you all only trying to fit the single binned spectrum overlapping with phase 0.5? Or are you all also fitting other phases that are dominated by day side emission? Please be clear

I also realize that the content of this section may change depending on the previous comments regarding the interpretation of the 4.5 micron "emission feature". I think regardless of the outcome, it should be made clear how critically the metallicity figure that is obtained depends on accurately determining the strength of the emission at 4.5 microns and that if it is due to systematics that this analysis no longer applies.

We fit the dayside spectrum only (phase 0.46 -0.54) and now state this explicitly in section 5.2. Our response to point 13 above addresses the issue of the significance of the different brightness temperatures at Hubble vs.  Spitzer wavelengths. Our retrieval analysis holds the temperature of the star fixed, and as shown in Figure 12, the dayside T/P profile is clearly inverted.  It is still true that there are some caveats about our conclusions from the retrieval, which are now bulleted at the end of section 5.2.1 (see our response to point 14 below).

@@

****

14. The authors close section 5.2.1 with a list of caveats about the error bars on this section and how the inferred [M/H] and [C/O] may be heavily skewed by the one 4.5 micron data point (from phase 0.5? or other bin? see previous comment). These caveats need to be more prominent considering how serious they may be to the interpretation. I think they need to be present in the abstract, and also they need to be bulleted here in the relevant section so that they are easy to catch for those that skim the paper instead of read it in depth.

#

We have reformatted section 5.2.1 to include the caveats as a bulleted list.  Since the caveats are now stated very prominently in 5.2.1 and in the summary bullet point in Section 8, we are confident that readers will not miss them. We did not add these points to the abstract because it is over the length limit, and we feel the impact of the paper will be greater if we focus scientific results in the abstract and leave the caveats in the main text.

@@

****

15. Section 5.2.2: Nightside spectrum. The authors fit a nightside spectrum at phase 0.1. One easy thing to do for comparison and to estimate or show error bars is to also fit a nightside spectrum at phase 0.9, which should be symmetric and obtain the same or similar results. I would ask that the authors please do this and report the results. I realize it might not be interesting because the fit already presented is not able to say much about the metallicity or the C/O ratio. This may also be a useful exercise for the dayside spectrum (fit at phase 0.4 and phase 0.6, or something similar).

A full atmospheric retrieval is actually quite computationally intensive. Since the nightside spectra are qualitatively similar (consistent with a blackbody at WFC3 wavelengths and lower temperature in the Spitzer bands), we do not expect any different result from fitting one phase bin over the other.  Moreover, as the referee notes, we already found that the nightside spectrum (at phase 0.1) is too imprecise to tightly constrain the metallicity or C/O. The spectrum at phase 0.9 is no higher precision. If the only purpose in running a retrieval is to verify that we can't tightly constrain metallicity and C/O, a full retrieval seems like overkill.

@@

17. The discussion of the magnetic field strength needed to produce a drag that sort of makes the GCM model work the best is very wishy washy. I understand that the authors are using order-of-magnitude expressions (as they state) but I think the magnetic field discussion is oversimplified and the conclusions are overstated. It also neglects to mention previous work attempting to directly measure/detect the effects of magnetic fields from planets. If the authors wish to discuss the magnetic fields, some mention of these previous works should be done. Significant mention about the shape of the magnetic field should also be prevalent. Furthermore, the planet is very close in to its star, and so there would likely be a complicated magnetic field structure due to the presence of the stellar magnetic field in the vicinity. This is not addressed or touched on when the authors assume the magnetic field is perpendicular to the flow of material.

If the authors want to keep a discussion of the magnetic field in the paper, this section should be significantly expanded and the caveats and assumptions more prominently listed. Otherwise, casual readers might over interpret this section to imply that a magnetic field is detected or that a magnetic field with a strength nice and similar to Jupiter's is the only possible explanation for the observable properties of the system with regards to its phase curve. It is the referee's preference however, that the magnetic field discussion is mostly scaled down or eliminated.

#

We expanded the discussion of magnetic fields according to the referee's suggestions. We think it is important to keep this section of the paper because it opens up discussion about a new way of measuring planet magnetic fields (studying their effects on the atmospheric dynamics, in contrast to previous work, which focused on star-planet interactions or planetary radio emission).  We put this discussion in a new subsection (6.1), added references to previous work, and mentioned the suggested caveats. We also clarified in the abstract that our estimate of the magnetic field is based on a back of the envelope calculation.

@@

****

18. Section 6: At the end of this section, the authors note that the GCM does not provide a good fit to the data, while the spiderman maps do much better. In that case, I wonder why such a large portion of the paper is devoted to something that doesn't work all that well (and a B-field inference drawn from it too). I think it's good to test the models and see what they can do when confronted with data, but at the same time I think the authors have over interpreted what has come out of the GCMs, as stated before.

#

We should have been more careful when describing whether the GCMs fit "well" or not.  Our intent was to say that none of the models are perfect: there is some degeneracy in the SPIDERMAN maps, and the GCM is too cold on the nightside.  Additional modeling and observations are required to robustly constrain the climate.  We reworded the paragraph in question to say this more directly.

More broadly, given that the GCM is a prediction, we don't expect it to fit as perfectly as a tuned model fit (like the SPIDERMAN models).  Our goal in this section was to determine which physical parameters (C/O, magnetic drag, etc.) are qualitatively important in shaping the spectrum.  The main take-away point is that the magnetic drag is the biggest factor in reducing the hotspot offset.  As we said in our response to point 17 above, we added some text emphasizing that the magnetic field inference is an order-of-magnitude estimate only, and more detailed modeling is needed for a precise characterization of the magnetic field.

@@

Thanks! We had trouble indentifying a single sentence in each bullet to bold, so this time we decided to leave it as is.

****

22. Several of these bullet points will likely need tweaking depending on the responses / extra work/interpretation from the previous comments. Similarly, the abstract will likely also need to be tweaked

Yes! We made a few small changes to the bulleted points in Section 8.

@@

Yes! We made a few small changes to the bulleted points in Section 8.

****

23. The last paragraph states that the authors have detected coruscation patterns influenced by the magnetic field. I think this is too strong a statement, and has not been exhaustively researched and concluded to be the only explanation here (see previous comments).

We softened the language here to suggest that magnetic fields *may* play a a role in shaping the circulation patterns.

@@

We softened the language here to suggest that magnetic fields *may* play a a role in shaping the circulation patterns.

===============================================
Minor and obnoxiously picky comments
1. Introduction, paragraph 2: Don't short change the small (but useful) handful of directly imaged planets when you say exoplanets are not resolved from their host stars.
#
Done.

2. Introduction paragraph 2: "The observations revealed large day-night..." should say "These observations revealed large day-night..."
#
Done.

3. Introduction paragraph 2: The authors list a bunch of references for Kepler that show evidence for reflected light and variable clouds. However, those references really only cover 2 Kepler planets (and one paper is more theoretical in nature). This is fine, but I would ask the authors to specifically name the planets in this case, since it's not widely observed.
#
There are actually 6 planets where dayside reflected light may be playing a role in the phase curve shape (see Paramentier et al. 2016), so rather than list all these we just keep the citations.

4.Section 2.3 Photometric Monitoring - The filter (Cousins R) should be in italics, as photometric passbands typically are.
#
FIXME - Greg, can you fix this?

5. Section 3.2.2 - Please put in parentheses next to the pixel sizes what this is in terms of arcseconds
#
Done.

6. Please clarify at the end of 3.3 that a \gamma = 1.1 for the power spectral density of red noise implies an equal amount of uncorrelated white noise and correlated noise.
#
Done.

7. Section 4.2: The authors state that they bin the light curve in intervals of 0.1 in orbital phase. Please also state the physical duration of these bins (i.e. a couple hours or so). This is made more difficult for the reader as there is no table with the system parameters present in the paper with which to easily look it up.
#
Done.

8. Section 4.5, Is the linear limb darkening parameter picked per bin? And is it initialized near some value (presumably from Claret)?
#
Yes, we fit a separate limb darkening parameter in each bin. We initialize our
MCMC on the best least squares fit (generally near 0.2). We added this
clarification to section 3.1.

@@

9. Table 5: I believe the third column needs to be multiplied by 100 like the second column was in order to get it as a % which is what it is labelled as. Is this true or am I misreading it (and by extension figure 9)?
#
Good catch - we corrected this (and changed the table format so that uncertainty is in a separate column rather than being listed twice).

10. I do not like that the authors cite Mansfield et al. (submitted) and Paramentier et al. (in prep) in section 5.2 while these papers are not accessible (and could change significantly with no version control on arXiv available!). The citations to these papers should be removed unless a publicly available version becomes available.
#
These papers are a part of a series related to emission spectra of the most highly irradiated planets, so we want to keep the references. We plan to post them to the arxiv at the same time, and then add the arxiv citations as soon as they are available.

11. 5.2.1 - Dayside spectrum: The authors infer a range of 23 +29 -13 times solar for the metallicity. In the summary section the authors state that they have > 1x solar at 3 sigma confidence. I would like this statement presented here as well, as I consider that a much more useful result than a number with a huge error bar.
#
Done.

12. Section 5.2.1: You infer from your fits a heat redistribution of 2.49 +0.14, -0.15, this is pretty close to the upper limits. I suppose since the prior was uniform and the upper bound on the prior is 3 sigma away this is fine and you can measure the peak and shape of the distribution regardless, but can the authors confirm that you're not significantly running into the walls of your prior?
#
FIXME -- Mike, what motivated the upper bound?

### 2018-04-05 ApJ_submit_v2/ms.tex
finished response

	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.  We fit the phase variation with a range of climate maps and find that a spherical harmonics model generally provides the best fit. The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 40$ K on the dayside. The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The inversion is not present on the nightside. The transmission spectrum is featureless, but consistent with the small transit depth variation expected from cloud-free models. Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.  We compare the phase curves to 3D general circulation models and find that magnetic drag effects are needed match the data; a back-of-the-envelope calculation suggests the strength of the magnetic field is $\sim1$ Gauss.  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.

@@

Exoplanets are so distant that they are generally not spatially resolved from their host stars, but it is still possible to reveal inhomogeneities in their atmospheres \added{by observing the total system flux}. One approach is to measure a phase curve, which consists of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet. This observation is sensitive to different longitudes at each orbital phase of the planet.  The first phase curve of an exoplanet was observed with \Spitzer\ for the hot Jupiter $\nu$ Andromedae b by \cite{harrington06}, followed by additional \Spitzer\ observations for about a dozen more systems \citep[cataloged in][]{parmentier17}.  These observations revealed large day-night temperature contrasts (in excess of 300 K), and eastward shifted peak brightness due to heat circulation, as predicted by 3D models \citep{showman02}.  These infrared measurements were complemented by optical phase curves from \Kepler\ that show evidence for reflected light from patchy and possibly variable dayside clouds with a range of compositions \citep{borucki09, demory13, hu15, armstrong16, parmentier16}. A \emph{spectroscopic} phase curve was observed for WASP-43b with \emph{Hubble}/Wide Field Camera 3 (\HST/WFC3) in the near-infrared, which provided the first phase-resolved measurements of an exoplanet's water abundance and thermal structure \citep{stevenson14, stevenson17}.

In this paper we present spectroscopic phase curve observations of the hot Jupiter WASP-103b, measured with \HST/WFC3 and Spitzer/IRAC. This planet is an ideal target for phase curve observations, with an orbital period of just 22 hours and an equilbrium temperature of 2500 K \citep{gillon14}.  Previous observations of WASP-103b's atmosphere revealed a blackbody-like dayside emission spectrum, with possible evidence for a $K_\mathrm{S}$-band emission feature \citep{cartier17, delrez18}. The optical transmission spectrum shows evidence for sodium and potassium absorption features that are consistent with expectations for a cloud-free atmosphere \citep{lendl17}.%, though other observations have shown a large optical scattering slope that is not fit well by theoretical models \citep{southworth16}.

@@

We calculated the transit model $T(t)$ with the \texttt{batman} package \citep{kreidberg15a}. Many of the physical parameters are tightly constrained by \cite{southworth15}, so we fixed the orbital period, time of inferior conjunction, orbital inclination, and ratio of semi-major axis to stellar radius to the previously published values ($P = 0.925545613$ day, $t_0 = 2456836.2964455\,\mathrm{BJD_{TDB}}$, $i = 87.3^\circ$, and $a/R_s = 2.999$). As a test, we fit for these parameters with the \Spitzer\ Channel 2 light curve, which has the best phase coverage and least systematic noise of the three data sets. We found that the transit parameters are consistent with the \cite{southworth15} results, so we proceeded with the remainder of the analysis holding those parameters fixed.  The free parameters for the transit model were the transit depth $r_p$ and a linear limb darkening parameter $u$. More complex limb darkening laws with additional free parameters were not merited according to the Bayesian Information Criterion (BIC).

@@

The BLISS sensitivity map is determined by bilinear interpolation over a grid of knots centered on the stellar flux. Each knot's sensitivity is calculated from the residuals to the light curve fit: the higher the flux values for data points near a given knot, the higher the detector sensitivity is at that position.  To avoid overfitting, we chose the grid scale such that bilinear interpolation performed better than nearest neighbor interpolation. For the $3.6\,\mu$m data, the grid scale was 0.008 pixel in both $x$ and $y$. For $4.5\,\mu$m, the scale was 0.022 pixel.  In addition to the intrapixel sensitivity variation, we fit the data for a linear trend in time. We tested a quadratic trend but did not find significant evidence for the additional model complexity based on the BIC.

\subsection{Best Fits and Uncertainties}
To determine the best fits, we performed a least-squares $\chi^2$ minimization for each wavelength and model. For a subset of these cases \added{where we wish to calculate 68\% confidence intervals}, we also performed a Markov chain Monte Carlo (MCMC) analysis to estimate parameter uncertainties. \added{These include the transit fits and the sine curve fit to the broadband phase curves.} We used \texttt{emcee} \citep{foremanmackey13} to fit the \HST/WFC3 light curves and differential evolution Monte Carlo for the \Spitzer\ fits \citep{braak06}. We ran the MCMC until convergence according to the Gelman-Rubin statistic. We initialized the MCMC chain on the best fit parameters and discarded the first 10\% of the chain as burn-in. MCMC techniques only produce robust uncertainties when the noise is normally distributed and white, so to account for correlated noise in the $3.6\,\mu$m light curve (described in \S\,\ref{sec:fitquality}) we fit the wavelet model from \cite{carter09} simultaneously with the other model parameters. We used a Haar wavelet and let the power spectral density of the red noise vary, following \cite{diamond-lowe14}. In our final fit, the noise power spectrum $1/f^\gamma$ had $\gamma = 1.1 \pm 0.1$.

\subsection{Goodness of Fit}
\label{sec:fitquality}
%WFC3 white: obs, exp rms (ppm) 172.140941477 122.002526515
%Ch1: rms obs, exp (ppm) 766.79959876 470.309808368
%Ch2: rms obs, exp (ppm) 636.908048707 639.675550854
We performed several tests of the quality of the light curve fits.  First we predicted the level of scatter in the light curves based on photon noise alone, then compared this value to the root-mean-square (rms) of the fit residuals.  For the spherical harmonics fit to the phase variation, the Spitzer 4.5 $\mu$m light curve rms reaches the expected photon noise limit (637 versus 640 ppm). The 3.6 $\mu$m light curve has significantly larger rms (767 versus 470 ppm), due to time-correlated red noise (discussed below). The expected photon-limited rms for the WFC3 spectrosopic light curves ranges from 430 - 530 ppm, and the measured rms was typically within 5\% of expectations for all spectroscopic channels.  For the WFC3 band-integrated white light curve, the rms was slightly larger than predicted (172 versus 122 ppm). There are a number of possible origins for this discrepancy, including imperfect background subtraction, variation in the position of the spatial scan on the detector, and loss of flux outside the extraction window. \added{In addition, the amplitude of the phase variation increases by 50\% over the WFC3 wavelength range, which leads to a small increase in the noise in the white light curve. To make an order of magnitude estimate for the amplitude of this effect, we calculated the standard deviation of the secondary eclipse depths in all wavelength channels. It is $\sim100$ ppm, which is comparable to the additional scatter we observed in the white light curve.}

@@

For the other orbital phases, we binned the light curve (with systematics
removed) in eight intervals of about 0.1 in orbital phase, with endpoints at
phases $0.06, 0.15, 0.25, 0.35, 0.44$ and $0.56, 0.65, 0.75, 0.85, 0.94$. These
endpoints were chosen to ensure that there is no contribution from in-transit or
in-eclipse data.  In each phase bin, we estimated the planet-to-star flux from
the mean value of the data points in the bin. To estimate the uncertainty, we
took the standard deviation of the points in the bin and added it in quadrature
to the standard deviation of the data points during secondary eclipse (phase
$0.46-0.54$), to account for the uncertainty in baseline stellar flux.  For the
$3.6\mu$m data, we also add red noise on the timescale of a phase bin, following
\cite{pont06}.  The phase-resolved emission spectra are shown in
Figure\,\ref{fig:spectra} and listed in Table\,\ref{table:spectra}. We show the
dayside spectrum in Figure\,\ref{fig:dayside}.

@@

%As illustrated in Figure\,\ref{fig:model_comparison}, the kinematic model is larger than the observed planet-to-star flux on the nightside, whereas the two temperature model overpredicts the flux at quadrature and underpredicts the dayside.

%However, this model may not be physically realistic: on the nightside, it produces much higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).

%The kinematic model has the hottest dayside temperature, and the two-temperature model has the smallest. The differences in peak temperature for the models we consider ranges from $630\,\mathrm{K}$ for \Spitzer\ Channel 1 to $1070\,\mathrm{K}$ for the broadband WFC3 light curve. The minimum nightside temperature is also model-dependent: for the WFC3 data, the two-temperature model predicts a nightside temperature of zero Kelvin, whereas the best fit kinematic model has a nightside temperature of $1980\,\mathrm{K}$.

@@

\section{Atmospheric Composition and Thermal Structure}
\label{sec:composition}
We characterized the planet's atmospheric composition by fitting 1D models to the phase-resolved emission spectra.  First, we modeled the planet flux as a simple blackbody to estimate the dayside brightness temperature and test for significant absorption or emission features. We then performed a more sophisticated grid-based retrieval to estimate the atmospheric metallicity, carbon-to-oxygen ratio, and thermal structure.

>>>>

	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.  The dayside planet-to-star flux ratios are $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.  We fit the phase variation with a range of climate maps and find that a spherical harmonics model generally provides the best fit. The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 40$ K on the dayside. The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The inversion is not present on the nightside. The transmission spectrum is featureless, but consistent with the small transit depth variation expected from cloud-free models. Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} = 23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.  We compare the phase curves to 3D general circulation models and find that magnetic drag effects are needed match the data; \added{a back-of-the-envelope calculation suggests the strength of the magnetic field is $\sim1$ Gauss.}  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.

@@

Exoplanets are so distant that they are \added{generally} not spatially resolved from their host stars, but it is still possible to reveal inhomogeneities in their atmospheres \added{by observing the total system flux}. One approach is to measure a phase curve, which consists of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet. This observation is sensitive to different longitudes at each orbital phase of the planet.  The first phase curve of an exoplanet was observed with \Spitzer\ for the hot Jupiter $\nu$ Andromedae b by \cite{harrington06}, followed by additional \Spitzer\ observations for about a dozen more systems \citep[cataloged in][]{parmentier17}.  These observations revealed large day-night temperature contrasts (in excess of 300 K), and eastward shifted peak brightness due to heat circulation, as predicted by 3D models \citep{showman02}.  These infrared measurements were complemented by optical phase curves from \Kepler\ that show evidence for reflected light from patchy and possibly variable dayside clouds with a range of compositions \citep{borucki09, demory13, hu15, armstrong16, parmentier16}. A \emph{spectroscopic} phase curve was observed for WASP-43b with \emph{Hubble}/Wide Field Camera 3 (\HST/WFC3) in the near-infrared, which provided the first phase-resolved measurements of an exoplanet's water abundance and thermal structure \citep{stevenson14, stevenson17}.

In this paper we present spectroscopic phase curve observations of the hot
Jupiter WASP-103b, measured with \HST/WFC3 and Spitzer/IRAC. This planet is an
ideal target for phase curve observations, with an orbital period of just 22
hours and an equilbrium temperature of 2500 K.  \added{WASP-103b is slightly
larger than Jupiter, with a mass and radius of $1.49\pm0.09\,M_\mathrm{Jup}$ and
$1.53^{+0.05}_{-0.07}\,R_\mathrm{Jup}$, respectively. The host star is a main-sequence F8 dwarf with an effective temperature of $6110 \pm 160\,$ K \citep{gillon14}.} Previous observations of WASP-103b's atmosphere revealed a blackbody-like dayside emission spectrum, with possible evidence for a $K_\mathrm{S}$-band emission feature \citep{cartier17, delrez18}. The optical transmission spectrum shows evidence for sodium and potassium absorption features that are consistent with expectations for a cloud-free atmosphere \citep{lendl17}.%, though other observations have shown a large optical scattering slope that is not fit well by theoretical models \citep{southworth16}.

@@

We calculated the transit model $T(t)$ with the \texttt{batman} package \citep{kreidberg15a}. Many of the physical parameters are tightly constrained by \cite{southworth15}, so we fixed the orbital period, time of inferior conjunction, orbital inclination, and ratio of semi-major axis to stellar radius to the previously published values ($P = 0.925545613$ day, $t_0 = 2456836.2964455\,\mathrm{BJD_{TDB}}$, $i = 87.3^\circ$, and $a/R_s = 2.999$). As a test, we fit for these parameters with the \Spitzer\ Channel 2 light curve, which has the best phase coverage and least systematic noise of the three data sets. We found that the transit parameters are consistent with the \cite{southworth15} results, so we proceeded with the remainder of the analysis holding those parameters fixed.  The free parameters for the transit model were a \added{wavelength-dependent} transit depth $r_p(\lambda)$ and linear limb darkening parameter $u(\lambda)$. More complex limb darkening laws with additional free parameters were not merited according to the Bayesian Information Criterion (BIC). \added{We initialized our MCMC chains on the least squares best fit parameters.}

@@

The BLISS sensitivity map is determined by bilinear interpolation over a grid of knots centered on the stellar flux. Each knot's sensitivity is calculated from the residuals to the light curve fit: the higher the flux values for data points near a given knot, the higher the detector sensitivity is at that position.  To avoid overfitting, we chose the grid scale such that bilinear interpolation performed better than nearest neighbor interpolation. For the $3.6\,\mu$m data, the grid scale was 0.008 pixel \added{(0.0098 arcsec)} in both $x$ and $y$. For $4.5\,\mu$m, the scale was 0.022 pixel \added{(0.027 arcsec)}.  In addition to the intrapixel sensitivity variation, we fit the data for a linear trend in time. We tested a quadratic trend but did not find significant evidence for the additional model complexity based on the BIC.

\subsection{Best Fits and Uncertainties}
To determine the best fits, we performed a least-squares $\chi^2$ minimization for each wavelength and model. For a subset of these cases \added{where we wish to calculate 68\% confidence intervals}, we also performed a Markov chain Monte Carlo (MCMC) analysis to estimate parameter uncertainties. \added{These include the transit fits and the sine curve fit to the broadband phase curves.} We used \texttt{emcee} \citep{foremanmackey13} to fit the \HST/WFC3 light curves and differential evolution Monte Carlo for the \Spitzer\ fits \citep{braak06}. We ran the MCMC until convergence according to the Gelman-Rubin statistic. We initialized the MCMC chain on the best fit parameters and discarded the first 10\% of the chain as burn-in. MCMC techniques only produce robust uncertainties when the noise is normally distributed and white, so to account for correlated noise in the $3.6\,\mu$m light curve (described in \S\,\ref{sec:fitquality}) we fit the wavelet model from \cite{carter09} simultaneously with the other model parameters. We used a Haar wavelet and let the power spectral density of the red noise vary, following \cite{diamond-lowe14}. In our final fit, the noise power spectrum $1/f^\gamma$ had $\gamma = 1.1 \pm 0.1$ \added{(implying an equal amount of white noise and correlated noise)}.  
\subsection{Goodness of Fit}
\label{sec:fitquality}
%WFC3 white: obs, exp rms (ppm) 172.140941477 122.002526515
%Ch1: rms obs, exp (ppm) 766.79959876 470.309808368
%Ch2: rms obs, exp (ppm) 636.908048707 639.675550854
We performed several tests of the quality of the light curve fits.  First we
predicted the level of scatter in the light curves based on photon noise alone,
then compared this value to the root-mean-square (rms) of the fit residuals.
For the spherical harmonics fit to the phase variation, the Spitzer 4.5 $\mu$m
light curve rms reaches the expected photon noise limit (637 versus 640 ppm).
The 3.6 $\mu$m light curve has significantly larger rms (767 versus 470 ppm),
due to time-correlated red noise (discussed below). The expected photon-limited
rms for the WFC3 spectrosopic light curves ranges from 430 - 530 ppm, and the
measured rms was typically within 5\% of expectations for all spectroscopic
channels.  For the WFC3 band-integrated white light curve, the rms was slightly
larger than predicted (172 versus 122 ppm). There are a number of possible
origins for this discrepancy, including imperfect background subtraction,
variation in the position of the spatial scan on the detector, and loss of flux
outside the extraction window. \added{In addition, the amplitude of the phase
variation increases by 50\% over the WFC3 wavelength range, which leads to a
small increase in the noise in the white light curve. To make an order of
magnitude estimate for the amplitude of this effect, we calculated the standard
deviation of the secondary eclipse depths in all wavelength channels. It is
$\sim100$ ppm, which is comparable to the additional scatter we observed in the
white light curve.}

@@

For the other orbital phases, we binned the light curve (with systematics
removed) in eight intervals of about 0.1 in orbital phase \added{(2.2 hours)}, with endpoints at
phases $0.06, 0.15, 0.25, 0.35, 0.44$ and $0.56, 0.65, 0.75, 0.85, 0.94$. These
endpoints were chosen to ensure that there is no contribution from in-transit or
in-eclipse data.  In each phase bin, we estimated the planet-to-star flux from
the mean value of the data points in the bin. To estimate the uncertainty, we
took the standard deviation of the points in the bin and added it in quadrature
to the standard deviation of the data points during secondary eclipse (phase
$0.46-0.54$), to account for the uncertainty in baseline stellar flux.  For the
$3.6\mu$m data, we also add red noise on the timescale of a phase bin, following
\cite{pont06}.  The phase-resolved emission spectra are shown in
Figure\,\ref{fig:spectra} and listed in Table\,\ref{table:spectra}. We show the
dayside spectrum in Figure\,\ref{fig:dayside}.

@@

@@

\section{Atmospheric Composition and Thermal Structure}
\label{sec:composition}
We characterized the planet's atmospheric composition by fitting 1D models to the phase-resolved emission spectra.  First, we modeled the planet flux as a simple blackbody to estimate the dayside brightness temperature and test for significant absorption or emission features. We then performed a more sophisticated grid-based retrieval to estimate the atmospheric metallicity, carbon-to-oxygen ratio, and thermal structure. \added{We also evaluated the climate based on the best fit \texttt{spiderman} temperature maps.}
